Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-27 appendix.Rmd
Fix paths for calling images in appendix

# read in metric names
phoenix_metrics <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-all_events.csv", header = FALSE)[-2,-1])

# read in metrics from crq analyses (target filtered)
phoenix_metrics_all_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
phoenix_metrics_pos_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
phoenix_metrics_neg_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])

# read in signficiance from permutation tests (target filtered)
phoenix_sig_all_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/metric_signif_all.csv", header = FALSE)[-1,-1])
phoenix_sig_pos_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/metric_signif_pos.csv", header = FALSE)[-1,-1])
phoenix_sig_neg_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/metric_signif_neg.csv", header = FALSE)[-1,-1])

# read in metrics from crq analyses (source and target filtered)
phoenix_metrics_all_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
phoenix_metrics_pos_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
phoenix_metrics_neg_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])

# read in signficiance from permutation tests (source and target filtered)
phoenix_sig_all_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/metric_signif_all.csv", header = FALSE)[-1,-1])
phoenix_sig_pos_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/metric_signif_pos.csv", header = FALSE)[-1,-1])
phoenix_sig_neg_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/metric_signif_neg.csv", header = FALSE)[-1,-1])

@@

# read in metric names
icews_metrics <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-all_events.csv", header = FALSE)[-2,-1])

# read in metrics from crq analyses (target filtered)
icews_metrics_all_targ <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
icews_metrics_pos_targ <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
icews_metrics_neg_targ <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])

# read in signficiance from permutation tests (target filtered)
icews_sig_all_targ <- t(read.csv("./results/secondary/icews/crqa/target/metric_signif_all.csv", header = FALSE)[-1,-1])
icews_sig_pos_targ <- t(read.csv("./results/secondary/icews/crqa/target/metric_signif_pos.csv", header = FALSE)[-1,-1])
icews_sig_neg_targ <- t(read.csv("./results/secondary/icews/crqa/target/metric_signif_neg.csv", header = FALSE)[-1,-1])

# read in metrics from crq analyses (source and target filtered)
icews_metrics_all_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
icews_metrics_pos_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
icews_metrics_neg_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])

# read in signficiance from permutation tests (source and target filtered)
icews_sig_all_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/metric_signif_all.csv", header = FALSE)[-1,-1])
icews_sig_pos_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/metric_signif_pos.csv", header = FALSE)[-1,-1])
icews_sig_neg_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/metric_signif_neg.csv", header = FALSE)[-1,-1])

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_all_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_all_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_all_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_all_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_pos_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_pos_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_neg_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_neg_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_all_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_all_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_pos_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_pos_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_neg_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_neg_DET.png")

>>>>

# read in metric names
phoenix_metrics <- t(read.csv("./results/secondary/phoenix/crqa/target-crqa_results-all_events.csv", header = FALSE)[-2,-1])

# read in metrics from crq analyses (target filtered)
phoenix_metrics_all_targ <- t(read.csv("./results/secondary/phoenix/crqa/target-crqa_results-all_events.csv", header = FALSE)[-1,-1])
phoenix_metrics_pos_targ <- t(read.csv("./results/secondary/phoenix/crqa/target-crqa_results-pos_events.csv", header = FALSE)[-1,-1])
phoenix_metrics_neg_targ <- t(read.csv("./results/secondary/phoenix/crqa/target-crqa_results-neg_events.csv", header = FALSE)[-1,-1])

# read in signficiance from permutation tests (target filtered)
phoenix_sig_all_targ <- t(read.csv("./results/secondary/phoenix/crqa/target-metric_signif_all.csv", header = FALSE)[-1,-1])
phoenix_sig_pos_targ <- t(read.csv("./results/secondary/phoenix/crqa/target-metric_signif_pos.csv", header = FALSE)[-1,-1])
phoenix_sig_neg_targ <- t(read.csv("./results/secondary/phoenix/crqa/target-metric_signif_neg.csv", header = FALSE)[-1,-1])

# read in metrics from crq analyses (source and target filtered)
phoenix_metrics_all_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target-crqa_results-all_events.csv", header = FALSE)[-1,-1])
phoenix_metrics_pos_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target-crqa_results-pos_events.csv", header = FALSE)[-1,-1])
phoenix_metrics_neg_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target-crqa_results-neg_events.csv", header = FALSE)[-1,-1])

# read in signficiance from permutation tests (source and target filtered)
phoenix_sig_all_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target-metric_signif_all.csv", header = FALSE)[-1,-1])
phoenix_sig_pos_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target-metric_signif_pos.csv", header = FALSE)[-1,-1])
phoenix_sig_neg_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target-metric_signif_neg.csv", header = FALSE)[-1,-1])

@@

# read in metric names
icews_metrics <- t(read.csv("./results/secondary/icews/crqa/target-crqa_results-all_events.csv", header = FALSE)[-2,-1])

# read in metrics from crq analyses (target filtered)
icews_metrics_all_targ <- t(read.csv("./results/secondary/icews/crqa/target-crqa_results-all_events.csv", header = FALSE)[-1,-1])
icews_metrics_pos_targ <- t(read.csv("./results/secondary/icews/crqa/target-crqa_results-pos_events.csv", header = FALSE)[-1,-1])
icews_metrics_neg_targ <- t(read.csv("./results/secondary/icews/crqa/target-crqa_results-neg_events.csv", header = FALSE)[-1,-1])

# read in signficiance from permutation tests (target filtered)
icews_sig_all_targ <- t(read.csv("./results/secondary/icews/crqa/target-metric_signif_all.csv", header = FALSE)[-1,-1])
icews_sig_pos_targ <- t(read.csv("./results/secondary/icews/crqa/target-metric_signif_pos.csv", header = FALSE)[-1,-1])
icews_sig_neg_targ <- t(read.csv("./results/secondary/icews/crqa/target-metric_signif_neg.csv", header = FALSE)[-1,-1])

# read in metrics from crq analyses (source and target filtered)
icews_metrics_all_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target-crqa_results-all_events.csv", header = FALSE)[-1,-1])
icews_metrics_pos_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target-crqa_results-pos_events.csv", header = FALSE)[-1,-1])
icews_metrics_neg_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target-crqa_results-neg_events.csv", header = FALSE)[-1,-1])

# read in signficiance from permutation tests (source and target filtered)
icews_sig_all_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target-metric_signif_all.csv", header = FALSE)[-1,-1])
icews_sig_pos_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target-metric_signif_pos.csv", header = FALSE)[-1,-1])
icews_sig_neg_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target-metric_signif_neg.csv", header = FALSE)[-1,-1])

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/target-windowed_all_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/target-windowed_all_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/target-windowed_pos_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/target-windowed_pos_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/target-windowed_neg_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/target-windowed_neg_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR.png")

@@

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET.png")
